The Sloan Digital Sky Survey: Two-dimensional Spectroscopic Reduction Pipeline

### 2011-03-17 doc/paper/paper2d.tex
Further comments and spatial tracing

Top level, call frm spcalib as of r54990 (20020301):  
 - Trace320crude, then fit with 5th-order polynomial.
 - The current trunk code does not match what was used for the SDSS legacy reductions, especially trace_cen.  What revision corresponds to the one used in the DR reductions??

 - Find initial fiber positions on each flat-field frame acquired during the 
plate observation sequence.  The final structure is a 320x2048 set of column 
positions representing the best estimate of the fiber column position in each 
row of the frame.
 - Given the camera optics the column positions bow inward towards the middle 
of the CCD frame.  The fibers are more closely spaced in column position for 
rows near the middle of the CCD.  The set of 21 rows about the center of the 
CCD is chosen to find the initial fiber positions.  A median\footnote{iterative
median, see appendix} is performed at each column positions, and a single row
is analyzed representing the median value per column.  The "median" central row
is cross correlated with a template representing expected fiber positions taking
into account fiber spacings and bundle separations.
- Given the best correlation offset (and minimum correlation value of ??), 
tweak each expected position from the template to the best empirical position 
in the median row by calculating a flux-weighted mean over a window of 6 pixels.

to locate the majority of profile peaks (see Figure ??? for examples of fiber
profiles in a typical SDSS frame).

Find approximate centers of all 320 fiber profiles for a single row, and note uncertain identifications due to bad pixels or falling off CCD frame.  The profile position is calculated as the interpolated peak in cross-sectional counts.  Cross correlate the identified positions with a template based on known fiber spacings.  
??  When did trace_cen move to parinfo standard ??

From initial centers move up and down the CCD images and "trace" the position centers by calculating the best count-weighted center over a fixed window based on the previous center.

Then perform a polynomial fit on all 320 fibers profiles as column positions versus row number.  A 4th order chebyshev?? polynomial is sufficient.  The polynomial fit is purely empirical and there is no optical model or other physical constraint on the polynomial solutions.

Next steps??

@@

\begin{table}
\begin{tabular}{ccc}
\hline
DR &  2d version & rerun ? \\
\hline
\hline
EDR - DR4 & 4\_?? & \\
DR5 & 5\_?? & \\
DR6 & ?? & 25 \\
DR7 & ?? & \\
\hline
\end{tabular}
\end{table}

@@

@@

@@

@@

@@

This spCFrame files contain the extracted spectra for a single CCD of a
single exposure. In general, each object has several blue exposures and
several red exposures. These spectra are still in the native wavelength
mapping, which is neither linear in wavelength nor log-wavelength.
However, the spectra are flux-calibrated, and deviant pixels are
rejected in the pixel mask (from the comparison with the other exposures).
The spCFrame file contains the following:
\begin{verbatim}
HDU #0 = Flux in units of 10^(-17) erg/s/cm^2/Ang [FLOAT]
HDU #1 = Inverse variance (1/sigma^2) for the above [FLOAT]
HDU #2 = Pixel mask [32-bit INT]
HDU #3 = Wavelength solution in log-10 Angstroms (vacuum) [FLOAT]
HDU #4 = Wavelength dispersion in units of (10e-4 log-10 wavelength)^(-1) [FLOAT]
         (these are the same units as in the combined-spectrum spPlate file)
HDU #5 = Plug-map structure from plPlugMapM file [BINARY FITS TABLE]
HDU #6 = Sky flux in units of 10^(-17) erg/s/cm^2/Ang [FLOAT]
\end{verbatim}

@@

@@

\begin{figure}
\figurenum{2}
\epsscale{0.9}
\plotone{SpecSecFull.ps}
\figcaption{Schematic layout of one of the SDSS double-spectrographs.
The light is fed from 320 fibers entering at the slithead (A), which
is in the center of the beam in this Schmidt camera design.
\label{fig2}
}
\end{figure}

@@

\begin{figure}
\figurenum{10}
\centering
\leavevmode
\includegraphics[width=0.8\columnwidth,angle=90]{plot_bestthru.ps}
%\epsscale{1.0}
%\plotone{plot_bestthru.ps}
\figcaption{ Throughput of the SDSS spectroscopic system,
as measured relative to the photon density expected above
the Earth's atmospheric by an aperture of 2.5-m with a 1.3-m
obscuration by the secondary mirror baffling.  These curves
are for plate 406 observed on MJD 51817, which was observed
in good-seeing photometric conditions shortly after
re-aluminization of the mirrors.
Solid curves are for spectrograph \#1, and dotted curves
for spectrograph \#2.
\label{fig10}
}
\end{figure}

>>>>

Top level, call frm spcalib as of r54990 (20020301):  
 - Trace320crude, then fit with 7th-order polynomial for column positions versus CCD row.
 - First, find all 16 bundles of 20 fibers by assuming known fiber (6.25 pixel)
and bundle (8 pixel) spacings.  Locate peaks by convolving the composite set of 21 central rows with a peak finding kernel\footnote{The kernel used was [-1, -1, 1, 2, 1, -1, -1]} that must match the known fiber pattern. ??please make more readble??
 - Starting with the initially determined column locations of all 320 fibers, 
improve estimate of centroids using a simple flux-weighted mean over a window of 6 pixels centered at the current position.  
 - Step in rows sequentially up and down using the previous row's positions as the initial window position in the flux-weighted mean.
 - Mask fibers which had problematic centroids, and replace centroids for all rows with interpolated values from neighboring traces.
 - Fit each spatial trace with a 7th order polynomial, with iteration and rejecting pixels which fall outside of 0.15 pixels from the best fit.
Next steps??

@@

\begin{table}
\begin{tabular}{ccc}
\hline
DR &  2d version & rerun ? \\
\hline
\hline
DR2 & 4\_10\_4  & 23 \\
DR3 & 4\_10\_4  & 23 \\
DR4 & 4\_10\_4  & 23 \\
DR5 & 4\_10\_4 & 23 \\
DR6 & 5\_3\_3  & 25 \\
DR7 & 5\_3\_12 & 26 \\
DR8 & 5\_3\_12 & 26 \\
\hline
\end{tabular}
\end{table}

@@

?? Refer to DR5? paper and Tremonti's SDSS paper which compares 
spectrophotometric colors to photo colors ??

@@

?? Drop galactic reddening, users should known when or when not to correct for it ??

@@

\bibitem[Subbarao et al. (2002)]{2002SPIE.4847..452S} SubbaRao, M., et al.\ 2002, SPIE, 4847, 452

@@

\bibitem[Adelman-McCarthy et al.(2007)]{2007ApJS..172..634A} 
Adelman-McCarthy, J.~K., et al.\ 2007, \apjs, 172, 634

\bibitem[Abazajian et al.(2009)]{2009ApJS..182..543A} Abazajian, K., et 
al.\ 2009, \apjs, 182, 543

@@

?? Alot of this is already published in the DR papers or on the DR websites ??
This spCFrame files contain the extracted spectra for a single CCD of a
single exposure. In general, each object has several blue exposures and
several red exposures. These spectra are still in the native wavelength
mapping, which is neither linear in wavelength nor log-wavelength.
However, the spectra are flux-calibrated, and deviant pixels are
rejected in the pixel mask (from the comparison with the other exposures).
The spCFrame file contains the following:
\begin{verbatim}
HDU #0 = Flux in units of 10^(-17) erg/s/cm^2/Ang [FLOAT]
HDU #1 = Inverse variance (1/sigma^2) for the above [FLOAT]
HDU #2 = Pixel mask [32-bit INT]
HDU #3 = Wavelength solution in log-10 Angstroms (vacuum) [FLOAT]
HDU #4 = Wavelength dispersion in units of (10e-4 log-10 wavelength)^(-1) [FLOAT]
         (these are the same units as in the combined-spectrum spPlate file)
HDU #5 = Plug-map structure from plPlugMapM file [BINARY FITS TABLE]
HDU #6 = Sky flux in units of 10^(-17) erg/s/cm^2/Ang [FLOAT]
\end{verbatim}

@@

?? Just refer to EDR paper, or one of the DR papers, and drop this section ??

@@

\begin{figure}
\figurenum{2}
\epsscale{0.9}
\plotone{SpecSecFull.ps}
\figcaption{Schematic layout of one of the SDSS double-spectrographs.
The light is fed from 320 fibers entering at the slithead (A), which
is in the center of the beam in this Schmidt camera design.
?? Drop this figure and refer to the Smee spectrograph paper ??
\label{fig2}
}
\end{figure}

@@

\begin{figure}
\figurenum{10}
\centering
\leavevmode
\includegraphics[width=0.8\columnwidth,angle=90]{plot_bestthru.ps}
%\epsscale{1.0}
%\plotone{plot_bestthru.ps}
\figcaption{ 
?? A similar figure is shown in the EDR paper, let's save space and refer to that??
Throughput of the SDSS spectroscopic system,
as measured relative to the photon density expected above
the Earth's atmospheric by an aperture of 2.5-m with a 1.3-m
obscuration by the secondary mirror baffling.  These curves
are for plate 406 observed on MJD 51817, which was observed
in good-seeing photometric conditions shortly after
re-aluminization of the mirrors.
Solid curves are for spectrograph \#1, and dotted curves
for spectrograph \#2.
\label{fig10}
}
\end{figure}
